---
title: "GNOSIS: Genomics explorer using statistical and survival analysis in R"
author:
- name: Lydia King
  affiliation: [
    "University of Galway, Ireland"
  ]
package: GNOSIS
output:
  BiocStyle::html_document:
    toc: false
vignette: >
  %\VignetteIndexEntry{GNOSIS Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# GNOSIS

`GNOSIS` is a `shiny` app that enables the exploration, visualisation and 
analysis of clinical and CNA summary data uploaded manually or obtained 
from cBioPortal, through `cBioPortalData`. GNOSIS provides an intuitive 
GUI with multiple tab panels supporting a range of functionalities including 
data upload and initial exploration, data recoding and subsetting, multiple 
visualisations, survival analysis, statistical analysis and mutation analysis.

# Installation

```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("GNOSIS")
```

# Loading the package

```{r,include=TRUE, results="hide", message=FALSE, warning=FALSE}
library(GNOSIS)
```

# Launching GNOSIS

```{r, eval=FALSE}
GNOSIS()
```

# Operation

For details on the implementation, layout and application of GNOSIS see the corresponding [publication](https://hrbopenresearch.org/articles/5-8#). 
Demonstration videos providing a walkthrough of GNOSIS are also provided on [Zenodo](https://zenodo.org/record/5788659). 

# Session Info

```{r}
sessionInfo()
```

```{r}
```
